Single-Molecule Orientation Determination With Polarized Illumination: Modeling and Microscope Design Comparison

### 2017-07-20 paper/paper/paper.tex
Changed mean and std to median and MAD.

We calculated $\sigma_{\Omega}$ on 100,000 approximately equally spaced points
on the unit sphere for each microscope design. A desirable microscope design
will have a small solid-angle uncertainty that is uniform for all fluorophore
orientations. To summarize and compare microscope designs we use the mean and
standard deviation of the solid-angle uncertainty at the sample points. Because
the solid-angle uncertainty admits unbounded values, we ignore the highest
percentile of the sample points and take the mean and standard deviation of the
0-99th percentile.

\section{Results}
\subsection{One-Arm Designs}\label{one-arm}
\begin{itemize}
\item Figure \ref{fig:single-arm} shows the results when we used a single
  objective to illuminate and detect.
\item We swept through the illumination and detection NA while keeping the
  incident power ($I_{\text{tot}}$) constant and found that the lowest mean and
  standard deviation of the solid-angle uncertainty occurs with a small
  illumination NA and a large detection NA.
\item A small illumination NA maximizes the ``contrast'' in the excitation
  efficiency, while a large detection NA maximizes the ``contrast'' in the
  detection efficiency. 
\end{itemize}

\begin{figure}[htbp]
\centering\includegraphics[width=\textwidth]{single-arm}
\caption{Epi-illumination microscope with varying NA and underfilling of the
  back aperture. a) Schematic of a single-arm four-frame epi-illumination
  microscope. b) Solid angle uncertainty for the microscope in a) when
  $I_{\text{tot}} = 1000$ photons. c) Mean of the solid-angle uncertainty as a
  function of illumination and detection NA. d) Standard deviation of
  solid-angle uncertainty as a function of illumination and detection NA. The
  microscope in a) and b) is indicated by a cross in c) and d).}
\label{fig:single-arm}
\end{figure}

\subsection{Two-Arm Designs}
\begin{itemize}
\item Figure \ref{fig:symmetric-widefield} shows the results when we used a
  symmetric widefield design. Both objectives serve as a an illumination and
  detection NA.
\item We swept through the NA and the angle between the objectives while
  considering steric constraints and while keeping the incident power constant. 
  We found that the lowest mean and standard deviation of the solid-angle
  uncertainty occurs with orthogonal arms with the highest possible NA. 
\end{itemize}

@@

\begin{itemize}
\item Figure \ref{fig:asymmetric-double} shows the results when we considered
  asymmetric light-sheet designs. We kept the two arms orthogonal and used light-sheet
  illumination. We swept the NA asymmetry and the dose asymmetry and found that the
  best results occur for symmetric designs. 
\item There is a tradeoff between solid-angle uncertainty mean and variance. You
  can slightly reduce the mean or variance by using an asymmetric design, but
  you pay for it. Reducing the mean increases the variance and vice-versa.
\item The best dual arm microscope design is a symmetric light-sheet
  illumination microscope with the largest possible detection NA.
\end{itemize}

@@

\subsection{Three-Arm Designs}
\begin{itemize}
\item Figure \ref{fig:triple-arm} shows the results when we considered
  symmetric light-sheet designs with a lower detection arm. We swept
  through the NA of the upper arms and NA of the lower arm.
\item The results show that the best designs have the largest possible detection
  upper and lower NA.
\item Note to Patrick: I used the same efficiencies for the upper and lower
  arms. I'm still thinking/unsure about the factor of $\sim$1/9 due to rolling
  shutter on the lower objective. If we do end up using this factor it will
  weight the importance of a large NA on the upper objectives.
\end{itemize}

>>>>

We calculated $\sigma_{\Omega}$ on 100,000 approximately equally spaced points
on the unit sphere for each microscope design. A desirable microscope design
will have a small solid-angle uncertainty that is uniform for all fluorophore
orientations. To summarize and compare microscope designs we use the median and
median absolute deviation (MAD) of the solid-angle uncertainty.

\section{Results}
\subsection{One-Arm Designs}\label{one-arm}
\begin{itemize}
\item Figure \ref{fig:single-arm} shows the results when we used a single
  objective to illuminate and detect.
\item We swept through the illumination and detection NA while keeping the
  incident power ($I_{\text{tot}}$) constant and found that the lowest median and
  MAD of the solid-angle uncertainty occurs with a small
  illumination NA and a large detection NA.
\item A small illumination NA maximizes the ``contrast'' in the excitation
  efficiency, while a large detection NA maximizes the ``contrast'' in the
  detection efficiency.
\end{itemize}

\begin{figure}[htbp]
\centering\includegraphics[width=\textwidth]{single-arm}
\caption{Epi-illumination microscope with varying NA and underfilling of the
  back aperture. a) Schematic of a single-arm four-frame epi-illumination
  microscope. b) Solid angle uncertainty for the microscope in a) when
  $I_{\text{tot}} = 1000$ photons. c) Median of the solid-angle uncertainty as a
  function of illumination and detection NA. d) MAD of solid-angle uncertainty
  as a function of illumination and detection NA. The microscope in a) and b) is
  indicated by a cross in c) and d).}
\label{fig:single-arm}
\end{figure}

\subsection{Two-Arm Designs}
\begin{itemize}
\item Figure \ref{fig:symmetric-widefield} shows the results when we used a
  symmetric widefield design. Both objectives serve as a an illumination and
  detection NA.
\item We swept through the NA and the angle between the objectives while
  considering steric constraints and while keeping the incident power constant.
  We found that the lowest median of the solid-angle uncertainty occurs the largest
  possible NA. We also found the increasing NA always lowers the MAD, but orthogonal
  arms are not always best. At large NA, it is advantageous to move the objectives
  as close or as far apart within steric constraints. 
\end{itemize}

@@

\begin{itemize}
\item Figure \ref{fig:asymmetric-double} shows the results when we considered
  asymmetric light-sheet designs. We kept the two arms orthogonal and used light-sheet
  illumination. We swept the NA asymmetry and the dose asymmetry and found that the
  best results occur for symmetric designs. 
\item There is a tradeoff between solid-angle uncertainty median and MAD. You
  can slightly reduce the mean or variance by using an asymmetric design, but
  you pay for it. Reducing the median increases the MAD and vice-versa.
\item The best dual arm microscope design is a symmetric light-sheet
  illumination microscope with the largest possible detection NA.
\end{itemize}

@@

\subsection{Three-Arm Designs}
\begin{itemize}
\item Figure \ref{fig:triple-arm} shows the results when we considered
  symmetric light-sheet designs with a lower detection arm. We swept
  through the NA of the upper arms and NA of the lower arm.
\item The results show that the best designs have the largest possible detection
  upper and lower NA.
\item Note to Patrick: I used the same efficiencies for the upper and lower
  arms. I'm still thinking/unsure about the factor of $\sim$1/9 due to rolling
  shutter on the lower objective. If we do end up using this factor it will
  weight the importance of a large NA on the upper objectives.
\item There is a small dip in the MAD when the upper and lower objectives have
  the same NA, but it is still better to use the largest possible lower
  NA. 
\end{itemize}
